---
title: "Problem Set 2"
output: pdf_document
date: "2022-09-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load("ggplot2")
```

## Fuel Economy
#1
```{r}
vehicles <- read.csv("~/Desktop/MSSP/homework/xuebuhui/vehicles.csv",header = T)
head(vehicles)
m1 <- vehicles[ c("year", "make", "model", "mpgData",
"phevBlended", "highwayE",
"fuelType", "fuelType1", "fuelType2",
"barrels08", "barrelsA08", "charge120", "charge240")]
m1$phevBlended <- as.logical(m1$phevBlended)
sum(m1$phevBlended)
head(m1[m1$phevBlended == FALSE, ])
```
```{r}
m1$fuelType <- as.factor(m1$fuelType)
levels(m1$fuelType)
m2 <- subset(m1, m1$fuelType %in% c("CNG","Diesel","Gasoline or E85","Gasoline or natural gas","Gasoline or propane","Midgrade","Premium","Premium or E85" ,"Regular"), drop = TRUE) 
m3 <- subset(m2,m2$year>=1984 & m2$year<=2023)
```
#analysis
Visualization of changes of Average annual petroleum consumption in barrels from 1984 to 2023.
```{r}
m4 <- aggregate(m3$barrels08, list(m3$year), FUN=mean)
ggplot(data=m4,mapping=aes(x=Group.1,y=x))+
  xlab("Year") +
  ylab("Average annual petroleum")+
  geom_line()+
  geom_point()
```
#2
Now, examine vehicle makers. Which ones have made the most progress?

```{r, fig.width=30,fig.height=11}
library("tidyverse")
m5 <- aggregate(m3$barrels08, list(m3$year,m3$make), FUN=mean)
p2 = ggplot(m5, aes(x = Group.1, y = x, color = Group.2)) + 
  geom_line( ) 
p2
```
```{r}
a <- function(x){
  max(x)-min(x)
}
m6 <- aggregate(m3$barrels08, list(m3$make), FUN=a)
ggplot(data = m6,aes(x = Group.1, y = x)) + 
  geom_bar(stat = 'identity')
```

## NASDAQ Composite

```{r}
IXIC21_22 <- read.csv("~/Desktop/MSSP/homework/xuebuhui/IXIC21_22.csv",header = T)
head(IXIC21_22)
Kplot<-function(OPEN,HIGH,LOW,CLOSE,DATE)
{
  N<-length(OPEN)
  w<-0.3 
  D<-OPEN-CLOSE 
  par(family='serif')
  
  plot(c(1:N),CLOSE,type='n',xaxt='n',xlab='Date',ylab='Adj.close',font.axis=1.5)
  
  title(main='NASDAQ',cex=2,col='black')
  for(i in 1:N)
  { 
    lines(c(i,i),c(LOW[i],HIGH[i]),col='black',lwd=1) 
    x<-c(i-w,i-w,i+w,i+w)
    y<-c(OPEN[i],CLOSE[i],CLOSE[i],OPEN[i]) 
    if(D[i]<0) 
    { 
      polygon(x,y,col='green',border='green') 
    } else 
    {
      polygon(x,y,col='red',border='red')
    }
  }

  
  Index<-seq(from=1,to=N,length=5)
  Index<-round(Index) 
  Text<-DATE[Index] 
  axis(side=1,Index,labels=Text,cex.axis=1)
}

a<-IXIC21_22

date<-a[,1]		
n<-length(date)	
open<-a[,2]		
high<-a[,3]		
low<-a[,4]		
close<-a[,5]		
DATE<-substr(date,1,10)			
Kplot(open,high, low,close,DATE) 

```

In a sentence or two, what does this plot show?
This plot reflects the general situation and price information of the stock market, which contains four data, the opening price, the highest price, the lowest price and the closing price. 

## Rural Capacity Index
#1.
```{r}
ruralCapacityData <- read.csv("~/Desktop/MSSP/homework/xuebuhui/ruralCapacityData.csv",header = T)
head(ruralCapacityData)
hist(ruralCapacityData$cap_index,main="",xlab="The Rural Capacity Index",breaks = 8)
a <- ruralCapacityData[,2:15]
fit <- lm(a$cap_index~.,data = a)
summary(fit)
```
Choose your other variables to reflect their contribution to the rural capacity index.
From the simplest linear regression analysis, it displays that "Population 25 years and older", "Population with a bachelors degree", and "Percent of population 25 and over with a bachelors degree" have contribution to the rural capacity indexs.

#2.
```{r}
x <- ruralCapacityData$per_over_25_with_bach
y <- log(ruralCapacityData$house_broadband)
fake <- data.frame(x,y)
fit2 <- lm(y~x,data = fake)
summary(fit2)
ggplot(data = fake,
aes(x = x, y = y)) +
geom_point() +
geom_smooth(method = "lm", se = FALSE)
```
```{r}
fake2 <- data.frame(x,y,ruralCapacityData$cap_index)
fit2b <- lm(ruralCapacityData$cap_index~x+y,data=fake2)
summary(fit2b)
```
#3
```{r}
pop_16 <- subset(ruralCapacityData, ruralCapacityData$pop_total < 16000)
head(pop_16)
pop_16_55 <- subset(ruralCapacityData,ruralCapacityData$pop_total > 16000 & ruralCapacityData$pop_total < 55000)
head(pop_16_55)
pop_55 <- subset(ruralCapacityData,ruralCapacityData$pop_total > 55000)
head(pop_55)
par(mfrow=c(1,3))
ggplot(data = pop_16,aes(x = County, y = cap_index))+geom_histogram(stat = 'identity')
ggplot(data = pop_16_55,aes(x = County, y = cap_index))+geom_histogram(stat = 'identity')
ggplot(data = pop_55,aes(x = County, y = cap_index))+geom_histogram(stat = 'identity')
```
What facets of each population subsection stand out to you, demonstrate them in your plots.
The small population counties show that they have smaller The Rural Capacity Indexs because the small population Capacity Index's highest frequency is 40-45. While as for the Median population and Large population, their highest frequencies are around 84-85.
```{r}
hist(pop_16$cap_index,main="",xlab="Cap Index of Small Poppulation",breaks = 10)
hist(pop_16_55$cap_index,main="",xlab="Cap Index of Median Poppulation",breaks = 10)
hist(pop_55$cap_index,main="",xlab="Cap Index of Large Poppulation",breaks = 10)
```

